% resume-a4.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2024 Todd C. Miller <Todd.Miller@sudo.ws> http://www.millert.dev/
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[a4paper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0mm}

% Adjust margins to 12.5mm on all sides
\addtolength{\oddsidemargin}{-12.5mm}
\addtolength{\evensidemargin}{-12.5mm}
\addtolength{\textwidth}{25mm}
\addtolength{\topmargin}{-12.5mm}
\addtolength{\textheight}{25mm}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{172mm}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{180mm}{l@{\extracolsep{\fill}}r}
\textbf{\large Kevin Juandi}  & +65 81205259\\
kevin.juandi@colorado.edu &  +62 85718605803 \\
kjuandi@gmail.com& https://github.com/Chiuchiyin\\
\end{tabular*}
\\

\vspace{0.25mm}

\resheading{Education}

\begin{itemize}
	\item
	\ressubheading{University of London}{Part-time distance learning}{Computer Science}{October 2022 - Present}
\end{itemize}

\begin{itemize}
	\item
	\ressubheading{University of Colorado}{}{Master of Science in Data Science}{March 2023 - June 2024}
\end{itemize}

\begin{itemize}
\item
	\ressubheading{Georg-August-Universität Göttingen}{}{Physics}{October 2012 - February 2022}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Georg-August-Universität Göttingen}{}{Teaching Assistant}{October 2017 - February 2022}
	\begin{itemize}
		\resitem{Part of the team tutoring freshmen for preparation of basic lab courses in classes of 30 students.}
		\resitem{Taught students to perform error calculation, writing lab reports in LaTeX and gnuplot for graph plotting.}
		\resitem{Supervised group of 6 conducting basic experiments.}
	\end{itemize}
\item
	\ressubheading{Max Planck Institute for Dynamics and Self-Organization
	}{}{Research Assistant}{October 2015 - November 2015}
	\begin{itemize}
		\resitem{Reverse engineered 3D ultrasound data stored in DICOM format to raw data.}
		\resitem{Processed the raw data to 3D object using freeglut.}
	\end{itemize}
\end{itemize}

\resheading{Skills}

\begin{description}
\item[Programming Languages:]
C/C{}\verb!++!, JavaScript, Unix Shell, R, Python
\item[Machine Learning Packages (Python):]
scikit-learn, TensorFlow, PyTorch
\item[Languages:]
Bahasa Indonesia, English, German, Mandarin, Hokkien
\item[Miscellaneous:]
Good understanding of mathematics, statistics and machine learning algorithms. 
\end{description}

\resheading{Personal Projects and Interest}

\begin{description}
\item[2023 - Present] Classification of heartbeats with machine learning.
\item[2022] GPT-2 based Donald Trump chatbot trained with 2020 presidential debate.
\item[Interests:] Generative AI (e.g. GAN and it's potential use in medicine), Natural Language Processing, Computer Vision, Non-linear Dynamics Simulation, Quantitative Epidemiology.

\end{description}


\end{document}
